Parsing Postfix log files

### 2009-03-28 doc/logparser-results.tex
Changes made after reading my paper.

XXX REUSE THE CONTENT FROM THE PAPER FOR THIS SECTION\@.

@@

\clearpage{}

@@

At the time of writing there are \numberOFrules{} different rules: the top
10\% recognise the vast majority of log lines, with the remaining log lines
split across the other 90\% of the rules (as shown in \graphref{rule hits
graph}).  Assuming that the distribution of log lines is reasonably
consistent over time, parser efficiency should benefit from trying more
frequently recognising rules before those that recognise less frequently.
To test this hypothesis three full test runs were performed with different
rule orderings:

@@

\Graphref{Parsing time relative to shuffled ordering graph} shows the
parsing times of optimal and reverse orderings relative to shuffled
ordering; the mean relative parsing times for different groupings of log
files are given in \tableref{Parsing time relative to shuffled ordering
table}.  Overall this optimisation provides a modest but worthwhile
performance increase of approximately 10\%, for a small investment in time
and programming.

@@

How any architecture scales as the number of rules increases is important,
but it is particularly important in this architecture because it is
expected that the typical parser will have a large number of rules.  There
are \numberOFrules{} rules in the full Postfix ruleset, whereas the minimum
number of rules required to parse the \numberOFlogFILES{} log files used
when generating the results in this thesis is \numberOFrulesMINIMUM{},
\numberOFrulesMINIMUMpercentage{} of the full ruleset.  The full ruleset is
larger because the Postfix parser is tested with \numberOFlogFILESall{} log
files, to improve its parsing and ensure it correctly parses logs generated
by later Postfix versions.  A second set of statistics was generated using
the minimum ruleset and compared to the statistics generated using the full
ruleset: the percentage parsing time increase when using the full ruleset
instead of the minimal ruleset for optimal, shuffled, and reversed
orderings is shown in \graphref{Percentage parsing time increase of maximum
ruleset over minimum ruleset}.

@@

It is clear from \graphref{Percentage parsing time increase of maximum
ruleset over minimum ruleset} that the increased number of rules noticeably
increases parsing time with reverse ordering, and to a lesser extent with
shuffled ordering.  The optimal ordering (where the rules that recognise
log lines most frequently are tried first) shows a mean increase of
\input{build/include-full-ruleset-vs-minimum-ruleset} in parsing time for a
\numberOFrulesMAXIMUMpercentage{} increase in the number of rules.  Log
files 22 and 62--68 show much smaller increases for shuffled and reversed
ordering than other log files do, because the majority of log lines in
those log files are parsed by Postfix components with a small number of
parsing rules, so removing unnecessary rules has little effect on the total
number of rules used.  These results show that the architecture scales very
well as the number of rules increases, and that optimally sorting the rules
is an important optimisation contributing to this scalability.

>>>>

@@

@@

At the time of writing there are \numberOFrules{} different rules: the top
10\% recognise \input{build/include-top-ten-hits}\% of the log lines, with
the remaining log lines split across the other 90\% of the rules (as shown
in \graphref{rule hits graph}).  Assuming that the distribution of log
lines is reasonably consistent over time, parser efficiency should benefit
from trying more frequently recognising rules before those that recognise
less frequently.  To test this hypothesis three full test runs were
performed with different rule orderings:

@@

\Graphref{Parsing time relative to shuffled ordering graph} shows the
parsing times of optimal and reverse orderings relative to shuffled
ordering; the mean relative parsing times for different groupings of log
files are given in \tableref{Parsing time relative to shuffled ordering
table}.  This optimisation provides a mean reduction in parsing time of
\input{build/include-optimal-ordering-parsing-time-reduction-other-logs}\%
with normal log files,
\input{build/include-optimal-ordering-parsing-time-reduction-logs-22-62-68}\%
when a mail loop occurs and the distribution of log lines is unusual.
Optimal rule ordering has other benefits, described in
\sectionref{scalability as the number of rules rises}.

@@

How any architecture scales as the number of rules increases is important,
but it is particularly important in this architecture because it is
expected that the typical parser will have a large number of rules.  There
are \numberOFrules{} rules in the full Postfix ruleset, whereas the minimum
number of rules required to parse the \numberOFlogFILES{} log files used
when generating the results in this thesis is \numberOFrulesMINIMUM{},
\numberOFrulesMINIMUMpercentage{} of the full ruleset.  The full ruleset is
larger because the Postfix parser is tested with \numberOFlogFILESall{} log
files, to improve its parsing and ensure it correctly parses logs generated
by later Postfix versions.  A second set of test runs was performed using
the minimum ruleset, and the parsing times compared to those generated
using the full ruleset: the percentage parsing time increase when using the
full ruleset instead of the minimal ruleset for optimal, shuffled and
reverse orderings is shown in \graphref{Percentage parsing time increase of
maximum ruleset over minimum ruleset}.

@@

Clearly the increased number of rules has a noticeable performance impact
with reverse ordering, and a lesser impact with shuffled ordering.  The
optimal ordering (where the rules that recognise log lines most frequently
are tried first) shows a mean increase of
\input{build/include-full-ruleset-vs-minimum-ruleset} in parsing time for a
\numberOFrulesMAXIMUMpercentage{} increase in the number of rules.  Log
files 22 and 62--68 show much smaller increases for shuffled and reversed
ordering than other log files do, because the majority of log lines in
those log files are parsed by Postfix components with a small number of
parsing rules, so removing unnecessary rules has little effect on the total
number of rules used.  These results show that the architecture scales very
well as the number of rules increases, and that optimally sorting the rules
is an important optimisation contributing to this scalability.
